Tulai

### 2025-07-28 paper/paper.qmd
minor edits to readme, update renv

```{r}
# Set the environment variable for GDAL
Sys.setenv(GDAL_CONFIG = "/path/to/your/conda/env/bin/gdal-config")

# Install the 'terra' package
install.packages("terra")

@@

A permutation MANOVA indicates that there is a significant difference in the lithic assemblage composition across the three excavation areas (`r PerMANOVA_results_inline`). We investigated this further using pairwise post-hoc tests and found that this significant difference is between TA and TP1, with the other two areas being statistically indistinguishable (@tbl-permanova )

# Correspondence Analysis (CA)
```{r}
# Example of a contingency table
lithic_data <- matrix(c(30, 20, 50, 
                        15, 25, 35,
                        45, 10, 30), 
                      nrow = 3, byrow = TRUE)
colnames(lithic_data) <- c("Cores", "Blades", "Flakes")
rownames(lithic_data) <- c("Unit1", "Unit2", "Unit3")

@@

# contribution plots
```{r}
# Example lithic data matrix
lithic_data <- matrix(c(30, 20, 50, 
                        15, 25, 35,
                        45, 10, 30), 
                      nrow = 3, byrow = TRUE)
colnames(lithic_data) <- c("Cores", "Blades", "Flakes")
rownames(lithic_data) <- c("Unit1", "Unit2", "Unit3")

>>>>

```{r}
# BM: What are these doing here? Not appropriate for a literate programming context. These are for interactive use, in the console.

# Set the environment variable for GDAL
# Sys.setenv(GDAL_CONFIG = "/path/to/your/conda/env/bin/gdal-config")

# Install the 'terra' package
# install.packages("terra")

@@

A permutation MANOVA indicates that there is a significant difference in the lithic assemblage composition across the three excavation areas (`r PerMANOVA_results_inline`). We investigated this further using pairwise post-hoc tests and found that this significant difference is between TA and TP1, with the other two areas being statistically indistinguishable (@tbl-permanova)

# Correspondence Analysis (CA)

```{r}
# Example of a contingency table
lithic_data <- matrix(c(30, 20, 50, 
                        15, 25, 35,
                        45, 10, 30), 
                      nrow = 3, byrow = TRUE)
colnames(lithic_data) <- c("Cores", "Blades", "Flakes")
rownames(lithic_data) <- c("Unit1", "Unit2", "Unit3")

@@

# Contribution plots

```{r}
# Example lithic data matrix
lithic_data <- matrix(c(30, 20, 50, 
                        15, 25, 35,
                        45, 10, 30), 
                      nrow = 3, byrow = TRUE)
colnames(lithic_data) <- c("Cores", "Blades", "Flakes")
rownames(lithic_data) <- c("Unit1", "Unit2", "Unit3")
